%% ---------------------------------------------------------------------------
%% proposal.tex
%%
%% Research Proposal, main document.
%%
%% ---------------------------------------------------------------------------
\documentclass[12pt,letterpaper]{article}
\usepackage[english]{babel}     % supports english, but default is
% \usepackage[spanish]{babel}
% include this if you want to import graphics files with /includegraphics

\usepackage{longtable}
\usepackage{ifpdf}
\usepackage[table]{xcolor}

\usepackage{anysize}
\marginsize{2.5cm}{2.5cm}{1cm}{1cm}
\usepackage{textcomp}
\usepackage{url}
\bibliographystyle{unsrt}
\usepackage{graphics}
\usepackage{amssymb}
\usepackage{graphicx}
%\usepackage{slashbox}
\usepackage[latin1]{inputenc}
\usepackage{tikz}
\usetikzlibrary{arrows,positioning}
% Color and strikethrough



\usepackage{color}
\usepackage{soul}

\usepackage{array}
\usepackage{makecell}

\usepackage{sectsty}
\allsectionsfont{\sffamily}

\definecolor{dblue}{RGB}{0,102,153}
\newcommand{\dB}[1]{\textcolor{dblue}{\textbf{#1}}}



\setlength{\parskip}{1em}

% Nombre del Estudiante
\newcommand{\scriptAuthor}{Daniel Moya Sánchez}
 
% Tí­tulo de la tesis
\newcommand{\scriptTitle}{Progress report \#2 for the project: Design of (ASIPs) for Approximate Computing} 


% Keywords
\newcommand{\scriptKeywords}{key, words, ...}

% Para el PDF (cambiar si se desea otras cosas a lo indicado arriba
\newcommand{\pdfAuthor}{\scriptAuthor}
\newcommand{\pdfTitle}{\scriptTitle} 
\newcommand{\pdfKeywords}{\scriptKeywords}


\tikzset{
    mynode/.style={rectangle,rounded corners,draw=black, top color=white, bottom color=yellow!50,very thick, inner sep=1em, minimum size=3em, text centered},
    myarrow/.style={->, >=latex', shorten >=1pt, thick},
    mylabel/.style={text width=7em, text centered} 
} 

\begin{document}
 
 \graphicspath{{./}{./fig/}}

 \input{./titlepage.tex}

%  \tableofcontents

 \clearpage

\section{Performed activities} \label{act}

\begin{enumerate}
 \item \textbf{Get to know the software platform}:  
 
 \item \textbf{Find appropiate error-tolerant applications}:  
 
 \item \textbf{Redact Design document}: The final design document was send to the professor.

 \end{enumerate}
 

\section{Change of scope} \label{change}



\section{Gained value analysis}

Table \ref{tab:gain} summarizes the gained value analysis. 

\begin{table}[h!]
\begin{center}
\caption{Revision History}
\resizebox{\textwidth}{!}{\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|c|c|} 
 \hline
\makecell{Activity\\ID}	&Activity	&Budget	&\makecell{\%Planned\\Value}	&PV	&AC	&\makecell{\%Completed\\work}	&EV	
&CPI	&SPI	&\makecell{Initial planned\\date}	&\makecell{Ending\\date}	&\makecell{Initial real\\date}	&\makecell{Real ending} \\ \hline


01	&\makecell{Get to\\ know the\\ software\\ platform}	&32	&100\%	&32	&30	&95\%	&$30.4$
&$1.01$	&0.95	&Week 1	&Week 3	&Week 1	&- \\ \hline

02	&\makecell{Find appropiate\\ error-tolerant\\ applications}	&32	&100\%	&32	&20	&70\%	&22.4
&1.12	&0.7	&Week 4	&Week 7	&Week 4	&- \\ \hline

06	& \makecell{Redact Design\\ document}	&8	&100\%	&8	&7	&100\%	&8
&1.14	&1	&\makecell{Week 3}	&\makecell{Week 4}	&\makecell{Week 3}	&\makecell{Week 5} \\ \hline
\end{tabular}}
\label{tab:gain}
\end{center}
\end{table}




\section{Encountered difficulties}



\section{Hard skills required/acquired}

Knowledge in the following software frameworks has been acquired:  Dlxsim, ModelSim and Xilinx ISE. 


\section{Soft skills required/acquired}

The following soft skills have been excercised:

\begin{itemize}
 \item Communication: Weekly remote communication has been performed with Jorge Castro for the guidance of this project, and
 with Sajjad Hussain to request technical aid in the server. With both, swift communication was achieved, each topic that
 was talked was resolved or clarified in very few messages (one or two at most).
 
 \item Self-Motivation: Given that there is no direct round-the-clock supervision, self-motivation has been key in working 
 continously in the laboratory sessions. 
 
 \item Problem Solving: The laboratory sessions provide several challenges given the theoretical aspects of assembly instructions and
 processor structure, which need to be addressed and later compared with a given solution.
 
 \item Problem Solving: Since there are a lot of approximable applications, careful analysis of existing applications has been key in
 reducing the search space to be manageable. 
\end{itemize}


\section{Learned lessons}

\begin{enumerate}
 \item S
\end{enumerate}



% Referencias del Background y el Related Work
\bibliographystyle{sty/plainurl}
\bibliography{references}



\end{document}

