%% ---------------------------------------------------------------------------
%% proposal.tex
%%
%% Research Proposal, main document.
%%
%% ---------------------------------------------------------------------------
\documentclass[12pt,letterpaper]{article}
\usepackage[english]{babel}     % supports english, but default is
% \usepackage[spanish]{babel}
% include this if you want to import graphics files with /includegraphics

\usepackage{longtable}
\usepackage{ifpdf}
\usepackage[table]{xcolor}

\usepackage{anysize}
\marginsize{2.5cm}{2.5cm}{1cm}{1cm}
\usepackage{textcomp}
\usepackage{url}
\bibliographystyle{unsrt}
\usepackage{graphics}
\usepackage{amssymb}
\usepackage{graphicx}
%\usepackage{slashbox}
\usepackage[latin1]{inputenc}
\usepackage{tikz}
\usetikzlibrary{arrows,positioning}
% Color and strikethrough



\usepackage{color}
\usepackage{soul}

\usepackage{array}
\usepackage{makecell}

\usepackage{sectsty}
\allsectionsfont{\sffamily}

\definecolor{dblue}{RGB}{0,102,153}
\newcommand{\dB}[1]{\textcolor{dblue}{\textbf{#1}}}



\setlength{\parskip}{1em}

% Nombre del Estudiante
\newcommand{\scriptAuthor}{Daniel Moya Sánchez}
 
% Tí­tulo de la tesis
\newcommand{\scriptTitle}{Progress report \#3 for the project: Design of (ASIPs) for Approximate Computing} 


% Keywords
\newcommand{\scriptKeywords}{key, words, ...}

% Para el PDF (cambiar si se desea otras cosas a lo indicado arriba
\newcommand{\pdfAuthor}{\scriptAuthor}
\newcommand{\pdfTitle}{\scriptTitle} 
\newcommand{\pdfKeywords}{\scriptKeywords}


\tikzset{
    mynode/.style={rectangle,rounded corners,draw=black, top color=white, bottom color=yellow!50,very thick, inner sep=1em, minimum size=3em, text centered},
    myarrow/.style={->, >=latex', shorten >=1pt, thick},
    mylabel/.style={text width=7em, text centered} 
} 

\begin{document}
 
 \graphicspath{{./}{./fig/}}

 \input{./titlepage.tex}

%  \tableofcontents

 \clearpage

\section{Performed activities} \label{act}

\begin{enumerate}
 \item \textbf{Familiarization with the software platform (ID 01)}: 
  
 \item \textbf{Find appropiate error-tolerant applications (ID 02)}: 

 \end{enumerate}
 

\section{Scope Changes} \label{change}

No scope changes have been made.

\section{Earned Value analysis}

Table \ref{tab:gain} summarizes the gained value analysis. 

\begin{table}[h!]
\begin{center}
\caption{Earned Value} \bigskip
\resizebox{\textwidth}{!}{\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|c|c|} 
 \hline
\makecell{Activity\\ID}	&Activity	&Budget	&\makecell{\%Planned\\Value}	&PV	&AC	&\makecell{\%Completed\\work}	&EV	
&CPI	&SPI	&\makecell{Initial planned\\date}	&\makecell{Ending\\date}	&\makecell{Initial real\\date}	&\makecell{Real ending} \\ \hline


01	&\makecell{Get to\\ know the\\ software\\ platform}	&32	&100\%	&32	&30	&95\%	&$30.4$
&$1.01$	&0.95	&Week 1	&Week 3	&Week 1	&- \\ \hline

02	&\makecell{Find appropiate\\ error-tolerant\\ applications}	&32	&100\%	&32	&15	&70\%	&22.4
&1.49	&0.7	&Week 4	&Week 6	&Week 4	&- \\ \hline


& Total	& &100\%	&72	&52	&84\%	&60.8
&1.16	&0.84	&	&	&	& \\ \hline
\end{tabular}}
\label{tab:gain}
\end{center}
\end{table}




\section{Difficulties Encountered}

\begin{itemize}
 \item The server errors have slowed down the progress of the activity 01, which should have been finished by the 
 last report.
 
 \item The personal computer used for work got a malfuction on a fan, which prevented the use of Linux (since Windows does
 have a fan control driver as opposed to Linux) and thus contributed to the slow progress on the laboratory sessions.
 
 \item Supervisor Jorge Castro was busy on week 6, situation that delayed the possible approximate applications review. 
\end{itemize}




\section{Hard Skills Required/Acquired}

\begin{itemize}
 \item Knowledge in the following software frameworks has been acquired:  Dlxsim, ModelSim and Xilinx ISE. 
 
 \item Basics of the following applications have been acquired: K-means, KNN, Canny (edge detector), Linear regression,
 Dbscan and ID3. 
\end{itemize}




\section{Soft Skills Required/Acquired}

The following soft skills have been excercised:

\begin{itemize}
 \item Communication: Weekly remote communication has been performed with Jorge Castro for the guidance of this project, and
 with Sajjad Hussain to request technical aid in the server. With both, swift communication was achieved, each topic that
 was talked was resolved or clarified in very few messages (one or two at most).
 
 \item Self-Motivation: Given that there is no direct round-the-clock supervision, self-motivation has been key in working 
 continously in the laboratory sessions and in the search of possible approximate applications.
 
\end{itemize}


\section{Lessons Learned}

It is very important to have tasks than can be parallelized because whenever something out of control (like the computer
malfunctioning) stops a task, one can still advance in another activity so the general impact on the schedule is not so big. 



% Referencias del Background y el Related Work
\bibliographystyle{sty/plainurl}
\bibliography{references}



\end{document}

