w%% ---------------------------------------------------------------------------
%% proposal.tex
%%
%% Research Proposal, main document.
%%
%% ---------------------------------------------------------------------------
\documentclass[12pt,letterpaper]{article}
\usepackage[english]{babel}     % supports english, but default is
% \usepackage[spanish]{babel}
% include this if you want to import graphics files with /includegraphics

\usepackage{longtable}
\usepackage{ifpdf}
\usepackage[table]{xcolor}

\usepackage{anysize}
\marginsize{2.5cm}{2.5cm}{1cm}{1cm}
\usepackage{textcomp}
\usepackage{url}
\bibliographystyle{unsrt}
\usepackage{graphics}
\usepackage{amssymb}
\usepackage{graphicx}
%\usepackage{slashbox}
\usepackage[latin1]{inputenc}
\usepackage{tikz}
\usetikzlibrary{arrows,positioning}
% Color and strikethrough



\usepackage{color}
\usepackage{soul}

\usepackage{array}
\usepackage{makecell}

\usepackage{sectsty}
\allsectionsfont{\sffamily}

\definecolor{dblue}{RGB}{0,102,153}
\newcommand{\dB}[1]{\textcolor{dblue}{\textbf{#1}}}



\setlength{\parskip}{1em}

% Nombre del Estudiante
\newcommand{\scriptAuthor}{Daniel Moya Sánchez}

% Tí­tulo de la tesis
\newcommand{\scriptTitle}{Project Plan} 


% Keywords
\newcommand{\scriptKeywords}{key, words, ...}

% Para el PDF (cambiar si se desea otras cosas a lo indicado arriba
\newcommand{\pdfAuthor}{\scriptAuthor}
\newcommand{\pdfTitle}{\scriptTitle} 
\newcommand{\pdfKeywords}{\scriptKeywords}


\tikzset{
    mynode/.style={rectangle,rounded corners,draw=black, top color=white, bottom color=yellow!50,very thick, inner sep=1em, minimum size=3em, text centered},
    myarrow/.style={->, >=latex', shorten >=1pt, thick},
    mylabel/.style={text width=7em, text centered} 
} 

\begin{document}
 
 \graphicspath{{./}{./fig/}}

 \input{./titlepage.tex}

%  \tableofcontents

 \clearpage

% El nombre del proyecto es preciso, conciso y no ambiguo
\section{Name of the project}

Design of Application Specific Instruction Set Processors (ASIPs) for Approximate Computing


% Se identifica claramente la institución donde se realizará el proyecto
\section{Name of the institution}
\begin{itemize}
	\item Chair for Embedded System (CES), Kalrsruhe Institute of Technology (KIT), 
	Germany, and 
	\item Laboratorio Sistemas Embebidos y Electrónica Digital (SEED-Lab) of Instituto 
	Tecnológico de Costa Rica (ITCR).
\end{itemize}




% Se identifica claramente qué información se puede publicar, qué
% información se puede compartir de manera limitada y qué
% información se puede compartir si se firma un acuerdo de
% confidencialidad.
\section{Confidentiality requirements}

Due to the academic nature of this project, there are no special confidentiality 
requirements. However, results will not be published until the end of the project's work.




% El problema se describe de manera detallada, identificando los
% antecedentes, el contexto, usuarios, restricciones así como otros
% aspectos relevantes para la resolución del mismo.

% OPCIONAL: Se presenta una descripción del estado del arte de
% las investigaciones sobre el tema en cuestión.
\section{Problem description}

An ASIP is a processor that use an application specific instruction set, this means 
that, although it can execute a wide range of applications, it is optimized for a 
specific one, in which the ASIP can execute with improved performance (for instance, 
energy consumption or execution time) compared to a General Purpose Proccesor (GPP). 
Although Application Specific Integrated Circuits (ASICs) present better performance 
results, ASIPs possess flexibility. Optimizations for an ASIP can be seen in different forms, 
including [CITA]: 

\begin{itemize}
 \item Instruction extension: Customized instructions can be made to extend the base Instruction Set Architecture (ISA).
 
 \item Inclusion or exclusion of predefined blocks: Not only specific software can be added 
 to extend an architecture but also customized hardware in the form of specialized blocks; 
 also, regular blocks not used can be excluded.
 
 \item Parameterization: Certain variables, such as cache sizes or number of registers, can 
 be customized to adjust for a specific application.
\end{itemize}

ASICs represent a hardware solution to a problem which is very limited and have high 
costs and a high time-to-market, but achieves the greatest performance. Contrary, GPPs 
are seen as a software solution which are very flexible but they are the least efficient. 
ASIPs are in the middle of these two as they balance flexibility and performance to have a 
good trade-off between those variables. 

ASIPs can also be used to adjust the balance between acceptable amount of error vs. the 
cost (economic, area, execution time) of an application; which is is the main focus of 
study of the project. Since different types of applications vary significantly in their 
requirements and specifications (e.g. where the error-resilient section is), different ASIPs 
have to be build for each one of them so that the best balance between cost savings and 
amount of error is achieved. This project focuses on that goal, to design ASIPs for a set 
of error-tolerant applications.

The environment in which the ASIPs will be developed consists in several software tools 
which include Design Compiler and Prime Time from Synopsys, ModelSim from Mentor 
Graphics,ASIPMeister, CoSy compiler, Xilinx ISE and the hardware platform will be a Xilinx 
Virtex-V board. Regardless these limitations, the project will allow for a custom hardware 
components choice with its design for specific sections. Also, for the error tolerant 
applications found, the software implementation and the tests for the general system will 
be able to be chosen between different options.

Since approximated computing is in its infancy, it still needs a lot of research and testing, 
so the users of the ASIPs developed will be the same groups of investigation of which this 
project is part of; it is expected that this helps to make approximated computing a more 
solid tendency.




\section{Objectives}

% El objetivo general es directamente trazable al problema planteado, es claro, conciso.
\subsection{General objectives}
Explore the design of Application-Specific Instruction Set Processors (ASIPs) for 
error-resilient applications.


% Los objetivos específicos son suficientes y consistentes con el
% objetivo general
\subsection{Specific objectives}

This project has the following specific objectives:

\begin{enumerate}
 \item Select 3 error tolerant applications to be evaluated. 
 
 \item Develop at least 3 instances of approximated hardware for tolerant error sections 
 for each of the selected applications. 
 
 \item Develop ASIPs configurations using specific approximated instructions for the 
 applications selected.
 
 \item Evaluate the selected applications on the designed ASIPs in terms of execution time, 
 area, and power consumption regarding the error introduced by the approximate 
 instructions.
\end{enumerate}



% La identificación de los involucrados y sus relaciones con el
% proyecto es detallada. Las relaciones se describen en detalle,
% señalando cuál es el interés del involucrado.
\section{Project stakeholders}

Due to this project belongs to a research project, there is only a few stakeholders, whom 
are described below:

\begin{itemize}
 \item Jorge Castro: He is the project's supervisor and he has the general idea about the 
 project itself and guides its course. He attempts to create new knowledge with the use of 
 ASIPs for error-tolerant applications, using approximate computing techniques, and that 
 their design become automated.
 
 \item Sajjad Hussain: He works with Jorge Castro on the general guidance of the project. 
 He supports any issue with the tools in Germany so that the process of using the 
 developing platform (ASIPMeister, Dlxsim, etc.) remains smooth. He has the same interest 
 as Jorge Castro regarding the project.  
 
 \item Jeferson González: He is the project's supervisor at the ITCR, and the person in 
 charge of the SEED laboratory, from where he occasionally provides guidance and 
 collaboration (such as lab equipment).
 
\end{itemize}



% Se presenta una descripción de la solución propuesta en
% correspondencia con el problema planteado y los objetivos.
% Se utilizan diagramas de bloques u otra información que permita
% visualizar la estrategia de solución al problema planteado.

% OPCIONAL: Se pressentan varias alternativas de solución a estudiar.
\section{Solution description}

\begin{figure}
\centering
\begin{tikzpicture}[node distance=1cm, auto]  
\tikzset{
    mynode/.style={rectangle,rounded corners,draw=black, very thick, minimum size=3em, text centered},
    myarrow/.style={->, >=latex', shorten >=1pt, thick},
    mylabel/.style={text width=7em, text centered} 
}  
\node[mynode] (manufacturer) {Application};  
\node[mynode, below left =3cm of manufacturer] (section1) {Section 1}; 
\node[mynode, below=2.16cm of manufacturer] (section2) {Section 2};
\node[mynode, below right=3cm of manufacturer] (section3) {Section 3};

\node[mynode, below=1cm of section1, dashed] (comment1) {\makecell{The entire section \\ can be approximated}};

\node[mynode, below left=3cm of section3] (instru1) {Instruction 1};
\node[mynode, below =2.16cm of section3] (instru2) {Instruction 2};
\node[mynode, below right=3cm of section3] (instru3) {Instruction 3};

\node[mynode, below=1cm of instru2, dashed] (comment2) {\makecell{The specific instruction \\ can be replaced for a \\ approximated version}};


\draw[myarrow] (manufacturer.south)  -- ++(0,-1) -|  (section1.north);
\draw[myarrow] (manufacturer.south)   -|  (section2.north);
\draw[myarrow] (manufacturer.south)  -- ++(0,-1) -|  (section3.north); 

\draw[->, >=latex', shorten >=1pt, thick, dashed]  (comment1.north) -|  (section1.south); 

\draw[myarrow] (section3.south)  -- ++(0,-1) -|  (instru1.north);
\draw[myarrow] (section3.south)   -|  (instru2.north);
\draw[myarrow] (section3.south)  -- ++(0,-1) -|  (instru3.north); 
 
 \draw[->, >=latex', shorten >=1pt, thick, dashed]  (comment2.north) -|  (instru2.south); 
 
\end{tikzpicture} 
\medskip
\caption{Expected situation to solve with this project} 
\end{figure}



% Los entregables con consistentes con los objetivos del proyecto y
% con los productos de un proyecto de ingeniería de software para
% efectos de desarrollo posterior o mantenimiento.
% Los entregables tienen un identificador único.
% Los entregables deben incluir:
%	- Documento de Requerimientos
%	- Documento de Diseño
%	- Plan de pruebas/Resultados de las preubas
%	- Otra documentación relevante: instrucciones de compilación,
% manuales de instalación, manual de usuario etc.
\section{Deliverables and criteria of acceptance}

The expected deliverables are the following:
\begin{table}
\begin{center}
\caption{Deliverables with the corresponding criteria of acceptance}
\begin{tabular}{ |c|c|c| } 
 \hline
Name & Description & Criteria of acceptance \\
 \hline
 Requirement 1.1 & Instances of approximated hardware & [criterio] \\ 
 Requirement 2.1 & Configuration of approximated ASIPs & [criterio] \\ 
 Requirement 3.1 & \makecell{Comparison and analysis of the \\
 obtained results (execution time,\\ area and power vs error)} & \makecell{Execution of the test \\ plan with satisfying results}  \\ %Plan Prueba
 Requirement 4.1 & Plan Project document & \makecell{Specifications given by the \\ professors for this document} \\
 Requirement 5.1 & Requirements document & \makecell{Specifications given by the \\ professors for this document} \\
 Requirement 6.1 & Design document & \makecell{Specifications given by the \\ professors for this document} \\
 Requirement 7.1 & Test plan document & \makecell{Specifications given by the \\ supervisor for this document} \\
 Requirement 8.1 & Final documentation & \makecell{Specifications given by the \\ professor for this document} \\
  
 \hline
\end{tabular}
\label{tab:del}
\end{center}
\end{table}



% Las cuatro áreas analizadas (personal, herramientas, procesos,
% insumos) son analizadas en detalle, identificando los riesgos más
% sobresalientes para cada una de esas áreas. Para cada riesgo se
% indica la probabilidad y el impacto para el proyecto.
\section{Risk analysis}
\begin{table}
\begin{center}
\caption{Risk analysis}
\begin{tabular}{ | c | c | c | c | } 
 \hline
 Risk & \makecell{Probability of \\ occurrence} & \makecell{Impact \\ (hours)} & \makecell{Risk exposure \\ (hours)} \\
 \hline
  \makecell{Illness or any special medical condition} & 0.5 & 8 & 4 \\ 
 \makecell{General server errors (missing files, \\ permission restrictions, etc)}   & 0.6 & 24 & 14.4 \\
 \makecell{Delays when acquiring the hardware}   & 0.25 & 8 & 2 \\
 \hline
\end{tabular}
\label{tab:risk}
\end{center}
\end{table}



% Las actividades propuestas son consistentes con los objetivos
% específicos.
% Las estimaciones de esfuerzos son proporcionales con la
% complejidad o el tamaño de las mismas.
% Se asigna un identificador único (código) a cada actividad.
\section{Activities and effort budget}

The table \ref{tab:act} takes in consideration a total of 216 engineering hours. 

\begin{table}
\begin{center}
\caption{Activities and effort budget}
\begin{tabular}{ | c | c | c | c | c | } 
 \hline
 ID  &Activity & \makecell{Engineering \\ hours} & \makecell{Risk reserve \\ (hours)} & \makecell{Total \\ (hours)} \\
 \hline
 001 & \makecell{Get to know the software platform} & 24 & 2 & 26 \\
 002 & \makecell{Find appropiate error-resiliant applications \\ and identify the sections that can be \\
  approximated} & 42 & 4 & 46  \\
 003 & \makecell{Implement the ASIPs in the error \\ tolerant applications found} & 50 & 3 & 53 \\
 004 & \makecell{Evaluate the results obtained with \\ a selected test plan} & 35 & 3 & 33 \\
 \hline
\end{tabular}
\label{tab:act}
\end{center}
\end{table}


% El cronograma incluye todas las actividades y las mismas no
% guardan una consistecia lógica para la construcción de los
% entregables.
% Se incluyen hitos para los entregables más sobresalientes.
% El nivel de granularidad de las actividades ofrece suficiente detalle.
% Al menos una actividad por semana.
\section{Schedule}

\begin{table}
\begin{center}
\caption{Schedule for the entire project}
\begin{tabular}{ | c | c | c | c | c | c | c | c | c | c | c | c | c | c | c | c | c |} 
 \hline
   & \multicolumn{16}{|c|}{Week} \\
 \hline
 Activity & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 & 11 & 12 & 13 & 14 & 15 & 16 \\ \hline
 \makecell{Reading the corresponding \\ literature about the \\ project and understanding \\ the general idea of ASIPs}
 & \cellcolor[HTML]{AA0044}  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\ \hline
 \makecell{Execution of the laboratory \\ script to get  to know \\ the software tools like \\ ASIPMeister, Dlxsim, etc}
 & \cellcolor[HTML]{AA0044}  & \cellcolor[HTML]{AA0044}  &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\ \hline
 \makecell{Delivery of the ``Plan Project'' \\ document}
 &  & \cellcolor[HTML]{AA0044}  &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\ \hline
 \makecell{Delivery of the ``Requirements'' \\ document}
 &  &   & \cellcolor[HTML]{AA0044} &  &  &  &  &  &  &  &  &  &  &  &  &  \\ \hline
 \makecell{Delivery of the ``Design'' \\ document}
 &  &   &  & \cellcolor[HTML]{AA0044} &  &  &  &  &  &  &  &  &  &  &  &  \\ \hline
  \makecell{Delivery of the ``Final report'' \\ document}
 &  &   &  &  &  &  &  &  &  &  &  &  &  &  &  & \cellcolor[HTML]{AA0044} \\ \hline
 \end{tabular}
\label{tab:schd}
\end{center}
\end{table}


% Referencias del Background y el Related Work
\bibliographystyle{sty/plainurl}
\bibliography{references}



\end{document}

